Random Matrix Theory Tools for the Predictive Analysis of Functional Magnetic Resonance Imaging Examinations

### 2023-04-07 paper/paper/SPIE/response_letter.tex

%%%%%% 16. Line 311: I see what they mean by "voxel time series" because of lines
%%%%%% 317-318, so it might be clearer to move those lines to directly after line 311,
%%%%%% so it is clear without having to read further.

17. The authors do a nice job of presenting the relevant results, but the
conclusions were rather general, being along the lines of "investigate the
sensitivity of choices made in the processing and analysis". That's an
important result, given previous work and shows that RMT might not "work" with
different data sets and processing workflows. The question is: what's the
takeaway: that the method is not one in which you can have a default set of
parameters that will generally give good results (like say, the recon-all
pipeline for FreeSurfer)? If RMT so sensitive to preprocessing and choice of
parameters, is this a useful method to be applied widely on fMRI data? It would
be good for this to be discussed and perhaps some recommendations given.
}

\noindent
\today, \\
Dear Dr. Gimi, \\

Thank you for your careful consideration of our manuscript
\emph{Random Matrix Theory Tools for the Predictive Analysis of Functional
Magnetic Resonance Imaging Examinations} submitted for publication in SPIE
Journal of Medical Imaging. We would especially like to thank the reviewer,
who and offered especially constructive and specific comments that we

@@

Reviewer comments 8, 9 noted some issues with vagueness involving descriptions
of the fMRI scans and runs in the text and tables. We hope these descriptions are now
unambiguous.

In response to comment 12, while we did, and still do take as given that our
reviewer and a reader of SPIE:JMI knows what features and feature extraction
are, we can see how at this point in the paper, it may not be clear
\textit{why} we are extracting features. We have added a short paragraph here
that we hope resolves this, and makes it clear we are comparing the predictive
utility of different features / feature extraction methods (and that "feature"
has the usual meaning in this context).

Comment 1 suggested expanding the introduction to Random Matrix Theory (RMT)
somewhat to better cover the basic aspects of RMT, and help with orienting
readers unfamiliar with the area. We have done this expansion, and hope that it
covers the basics both in a way that presumes neither too little nor too much
from readers (always a very difficult balance to strike with something like
RMT, unfortunately).

Finally, comment 17 suggested (by our reading) to opt for less caution and make
a stronger recommendation in our conclusions.

### 2023-04-07 paper/paper/SPIE/article.tex
WIP

\color{cyan}
Previous studies have not explored the sensitivity of RMT-based analyses to
analytic decisions. It is far too early to say whether RMT may prove fruitful
for understanding fMRI, however, we hope our analyses show that, \textit{if}
RMT has such potential, that potential must be contextualized by the analytic
decisions involved. Absent this context, we advise caution with regard to
claims that RMT offers insights into fMRI analyses.

>>>>

\color{cyan}
Previous studies have not explored the sensitivity of RMT-based analyses to
analytic decisions. It is far too early to say whether RMT may prove fruitful
for understanding fMRI, however, we hope our analyses show that, when RMT has
such potential, that potential must be contextualized by the analytic decisions
involved. Absent this analytical context, we advise considerable caution with
regard to claims that RMT offers insights into fMRI analyses.
